---
title: "Growth chamber conditions"
author: "Romain Garrigues"
date: "12-12-2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# Humidity

## Experimentals conditions

In growth chamber we have *Fagus* and *Populus*. The goal of this experiment is to study the Bud-Burst timing under optimal conditions (40-60% of Humidity and 22°C), after different timing of leaves-out and bud sampling for Transcriptomic and metabolomic analysises. So, we need to be bteween 40%-60% in growth chamber, for the relative himidity. The temperature needs to be at **22°C**. 

## Data

```{r}
# path = "./HOBOware/test_dataset.csv" or dataset <- read.csv("./HOBOware/test_dataset.csv", sep=",")

dataset <- read.csv("./HOBOware/test_dataset.csv", sep=",")
```

They are the commands to open the source of the datasel. 

The next part is to see the complet dataset, then to select only the dataset from the row 3909 to the end (December month). I created the "december_dataset" to focus only on the last month.

```{r}

View(dataset)

View(dataset[-c(1:3908), ])

december_datase <- dataset[-c(1:3908), ]

```

## Method

The dataset is done, now we need to obtain the graph for the humidity in all the month of december. To do that we are going to use the package **ggplot**.

```{r}
# install.packages("ggplot2")
# library("ggplot2")

# format(as.Date(december_datase$Date,format="%m/%d/%y"), format = "%d")

plot(format(as.Date(december_datase$Date,format="%m/%d/%y"), format = "%d"), december_datase$RH, xlab= "Date", ylab ="RH", abline(h=c(40, 60),col="red"))
```



## TODO 

- [x] Plot RH chart 
- [x] add 60 & 40 RH lines 
- [ ] Use GGplot for better visualisation
- [ ] Remove the first row of the CSV file
- [ ] add small multiples


## Results

```{r}

```

